Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-06 paper/paper.tex
pass on comments

\Mar{@Lucas/Guilheme, há algo o que remover? talvez ``window:64''?
  Qual a correspondencia de ``flags:S,12'' com ``flags:S''? Por favor,
  respondam isto logo.}  \Gui{}

@@

Active reconnaissance is a method used by malicious individuals to
collection information about a computing system to determine potential
vulnerabilities. Active reconnaissance is a preliminary step towards
an actual attack. The most popular technique is to ``scan'' open ports
in a host. A Ping Scan is a very common type of port scan based and it
is based on the ICMP protocol. \Mar{@Lucas, acima falamos de
  porta. Abaixo nao falamos de porta, apenas de maquina. Vc. pode ser
  mais especifico? ->}To scan a network, an attacker sends a several
ICMP Echo requests addressed to a range of IP addresses in the network
and checks which ones respond to the requests. This allow the attacker
to know which machines are active in the network, then it can choose
one of them to attack.

>>>>

\Mar{@Lucas/Guilheme, há algo o que remover? talvez ``window:64''?
  Qual a correspondencia de ``flags:S,12'' com ``flags:S''? Por favor,
  respondam isto logo.}  \Gui{O window:64 seria removido sim.}
  \Luc{O segundo campo da opção flags define flags que serão ignoradas. Nesse caso a regra procura por pacotes onde apenas a flag S está 'setada', independentemente do valor das flags 1 e 2. Portanto a regra gerada pode capturar coisas diferentes da regra original. A inferencia do "12" n pode ser feita apenas a partir do pacote de entrada, precisariamos tratar isso.}

@@

Active reconnaissance is a method used by malicious individuals to
collection information about a computing system to determine potential
vulnerabilities. Active reconnaissance is a preliminary step towards
an actual attack. The most popular technique is to ``scan'' open ports
in a host. A Ping Scan is a very common type of port scan based and it
is based on the ICMP protocol. \Mar{@Lucas, acima falamos de
  porta. Abaixo nao falamos de porta, apenas de maquina. Vc. pode ser
  mais especifico? ->}
  \Luc{De fato estamos falando de duas coisas diferentes, mas ambas são exemplos de 'active reconnaissance'. Primeiramente citamos o port scanning, q tem o objetivo de encontrar portas abertas em uma maquina especifica. Depois falamos do ping scan, q tem o objetivo de encontrar ip's ativos numa rede.} To scan a network, an attacker sends a several
ICMP Echo requests addressed to a range of IP addresses in the network
and checks which ones respond to the requests. This allow the attacker
to know which machines are active in the network, then it can choose
one of them to attack.
